\input{title.tex}

### 2022-05-04 docs/papers/01_manuscript/02_structures.tex
feat(institution-context): appendix sec1

\begin{figure*}[!h]
    \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:scheme87}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Since the YRCC does not use but monitor water, the provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdraw from the Yellow River restricted by specific quotas, each stakeholder seperatly develop by planning and using fundamental water resources. However, the natural hydrological processes are connected. Although the institutions focus mainly on the surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.'), through systematic socio-hydrological processes within the YRB.
		\textbf{C.} Institutional shifts and following structures changes. (1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply water use licences from the YRCC (the connections between the red and yellow circles).
	}
	\label{structure}
\end{figure*}

>>>>

\begin{figure*}[!h]
    \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Since the YRCC does not use but monitor water, the provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdraw from the Yellow River restricted by specific quotas, each stakeholder seperatly develop by planning and using fundamental water resources. However, the natural hydrological processes are connected. Although the institutions focus mainly on the surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.'), through systematic socio-hydrological processes within the YRB.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix S1}). (1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply water use licences from the YRCC (the connections between the red and yellow circles).
	}
	\label{structure}
\end{figure*}

### 2022-05-04 docs/papers/01_manuscript/04_discussion.tex
feat(institution-context): appendix sec1

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:S3-3}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

>>>>

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{Appendix S3} Figure~\ref{fig:S3-3}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

### 2022-05-04 docs/papers/02_appendix/01_institution_context.tex
feat(institution-context): appendix sec1

% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation). Currently, a major overhaul is in the planning stages. Major shifts of the institution can be analyzed by using the 1987 and 1998 documents. It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.

\textbf{The official documents in 1987 clearly convey the following key points:}
\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
\begin{itemize}
	% 该政策面向的目标是各省（区域），黄委会没有被提及
	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
	% 政策制定的首要考虑是解决断流问题
	\item Drying-up of the river is identified as the first consideration of this institution.
	% 各省被鼓励在此配额下制定自己的用水计划
	\item Provinces are encouraged to develop their own water use plans based on a quota system.
	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
	\item Water in short supply is a common phenomenon in relevant provinces (regions).
\end{itemize}

\textbf{The official documents in 1998 clearly convey the following key points:}
\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
\begin{itemize}
	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
	% 各省需要
	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
	% 强调以总量确定供给，以供给决定需求。
	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
\end{itemize}

% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008. By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).

\begin{figure}[!htb]
    \centering
    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
	\caption{
		Overview of water allocation institutions.
		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
	}
    \label{fig:world}
\end{figure}

\begin{figure}[!htb]
    \centering
	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
	\caption{
		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
		A top-down water resources allocation scheme in China (a case study of the YRB).
		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
		% 利益相关者是各省
		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development. Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
	}
	\label{fig:framework}
\end{figure}

>>>>

% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
Since 1982, administrations attemptted to design a quota institution, and the 2008 document marked the maturity of the scheme (complete establishment of basin-level, provincial, and district water quotas).
Between the period, two significant institutional shits can be analyzed by using the 1987 (87-WAS) and 1998 (98-UBR) documents.

% It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the depletion of the Yellow River.

The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:

\begin{itemize}
	% 该政策面向的目标是各省（区域），黄委会没有被提及
	\item The policy is aimed at related provinces (or regions in the same administrative level).
	% 政策制定的首要考虑是解决断流问题
	\item Depletion of the river is identified as the first consideration of this institution.
	% 各省被鼓励在此配额下制定自己的用水计划
	\item Provinces are encouraged to develop their own water use plans based on a quota system.
	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
	\item Water in short supply is a common phenomenon in relevant provinces (regions).
\end{itemize}

The official documents in 1998
(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:

\begin{itemize}
	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
	% 各省需要
	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
	% 强调以总量确定供给，以供给决定需求。
	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
\end{itemize}

% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
% On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008. By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).

\begin{figure*}[!htb]
    \centering
    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
	\caption{
		Overview of water allocation institutions.
		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
		\textbf{A.} Major river basins in the world with water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed since 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998) \cite{speed2013}.
		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system.
		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
	}
    \label{fig:world}
\end{figure*}

% 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{structure}~C.

\begin{table*}
    \centering
    \small
    \caption{Water quotas assigned in the 87-WAS}\label{tab:quota}
	\resizebox{\linewidth}{!}{
    \begin{tabular}{p{0.24\linewidth}llllp{0.1\linewidth}lllll}
	\hline
	Items (water volume, billion $m^3$)                    & Qinghai & Sichuan & Gansu   & Ningxia & Inner Mongolia & Shanxi  & Shaanxi & Henan   & Shandong & Jinji  \\
	\hline
	Demands in water plan                                                & 35.7    & 0       & 73.5    & 60.5    & 148.9          & 115     & 60.8    & 111.8   & 84       & 6      \\
	Quota designed in 1983                                               & 14      & 0       & 30      & 40      & 62             & 43      & 52      & 58      & 75       & 0      \\
	Quota assigned in 1987                                               & 14.1    & 0.4     & 30.4    & 40.0    & 58.6           & 38.0    & 43.1    & 55.4    & 70.0     & 20     \\
	Average water consumption from the Yellow River from 1987-2008       & 12.03   & 0.25$^a$   & 25.80   & 36.58   & 61.97          & 21.16   & 11.97   & 34.30   & 77.87    & 5.85$^a$  \\
	Proportion of water from the Yellow River in total water consumption & 48.12\% & 0.10$^b$\%  & 30.79\% & 58.45\% & 47.82\%        & 73.55\% & 44.39\% & 24.77\% & 34.41\%  & 3.11\%$^b$ \\
    \hline
    \end{tabular}}
	\footnotesize[a]\leftline{{Calculated by data from 2004 to 2017.}}\\
	\footnotesize[b]{\leftline{The share is too small, thus the provinces (or region) Sichuan and Jinji not to be considered in this study.}}
\end{table*}
